Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher

### 2016-03-29 pets2017-paper/pets2017-paper.tex
procedure and recruitment.

After users completed the browsing tasks or have spent the rest of the time
trying to configure Tor Browser, we interviewed participants about their experience.
We asked three standard questions asking about their general experience, 
confusing interface features, and soliciting feedback for improvements. We followed up
with specific questions we had for a particular participant from observing their screen. 
This was to verify any hypothesis we had about the participant (i.e. ``they didn't know what to do on window 3'').

@@

\subsubsection{Recruitment}
\subsubsection{Procedure}
\subsubsection{Results}

@@

\section{Quantitative User Recruitment Posting}
\label{qualitative-recruitment}
We are recruiting up to 40 participants for a user study at UC Berkeley. The experiment will involve basic Internet browsing tasks. You are not eligible if you have participated in a previous session on 3/23.\\

>>>>

After users completed the browsing tasks or have spent the rest of the time
trying to configure Tor Browser, we interviewed participants about their experience.
We asked three standard questions asking about their general experience, 
confusing interface features, and soliciting feedback for improvements. We followed up
with specific questions we had for a particular participant from observing their screen. 
This was to verify any hypothesis we had about the participant (i.e. ``they didn't know what to do on window 3'').  
After their interview, participants were informed that the experiment was over and 
given their payment of \$30.

@@

\subsubsection{Recruitment}
We recruited 20 users for each censorship environment
and interface combination, resulting in a total of 120 users. This decision 
was due to both data analysis considerations (large enough to have good effect size, 
with a minimum of 20 to be able to assume normal distributions) and funding
limitations.

We recruited half of our users from Craigslist, and half of our participants from 
the Xlab participant pool. It is standard for Xlab experiments to be run with Xlab
participants, who have been verified of their identity and have good attendance
rate. Although Xlab participants are not limited to UC Berkeley students and staff,
a majority of the participants are from campus. For this reason, we chose to recruit 
half of our participants from Craigslist to ensure a diverse set of participants. 
The recruitment text can be found in Appendix \ref{quantitative-recruitment}.

We chose our participants on who had responded to our listing first and their
availability for experiment sessions. We collected their demographic information
with an exit survey that participants took after the experiment.

Out of our {\color {red} TODO} participants, ages ranged from {\color {red} TODO}
(sigma = {\color {red} TODO}). {\color {red} TODO} of our participants had at least
a college education, and the most common jobs included {\color {red} TODO} and
{\color {red} TODO}.

\subsubsection{Procedure}
Similarly to the qualitative experiment, we conducted a quantitative evaluation 
of the interface by creating an environment  for users to interact with the 
configuration interface in a censored environment. The focus of this environment 
was to collect a dataset of metrics to evaluate the two interfaces.

The 1-hour, multi-participant procedure begins when all participants are sitting at their
respective computers in Xlab. Each computer is equipped with an old or modified version
of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording). 
Participants are firstly informed of the risks of the study and consenting to data collection.  At
this time, participants are given the chance to leave the laboratory if they do not consent to 
the experiment conditions. When every participant left in the room has turned in their consent
form, the experiment formally begins. A researcher informs the participants that they are in a
simulated censorship environment, where some websites and services are blocked. 
For the full script of what participants have heard, see Appendix \ref{quantitative-script}. We
instruct them to visit a sample blocked website on a non-Tor browser of their choice to illustrate 
the situation.

After illustrating the censorship environment, participants are asked to 
complete a worksheet that asks to visit one blocked website. 
Similar to the qualitative study, we chose Wikipedia's featured article of the day 
as the blocked website because the familiarity 
that most users have with these websites makes the browsing task relatively easy, 
which focuses participants' attention to configuring Tor Browser.

After instructions, researchers maintained minimal interactions with the participants, 
only answering logistical questions. Participants had an 
average of 40 minutes to complete their worksheet. 
The participants do not know the details of their censorship environment,
only that they are actively being censored. Participants needed to configure Tor Browser to 
circumvent the simulated censorship.

After users completed the browsing tasks, they take a short exit survey (Appendix \ref{quantitative-exit-survey})
collecting their demographics. All users were instructed to sit until the end of the experiment,
regardless of when they had completed their task. This was to ensure that others were not 
aware of when other participants had finished their tasks. After the 40 minutes were up, 
participants were officially informed that their time was up, and were given their payment of 
\$30.

\subsubsection{Results}

@@

\section{Quantitative User Recruitment Posting}
\label{quantitative-recruitment}
We are recruiting up to 40 participants for a user study at UC Berkeley. The experiment will involve basic Internet browsing tasks. You are not eligible if you have participated in our previous sessions.\\
